Writing News Captions with Bags of Attention

### 2019-10-27 paper/paper.tex
Add result for RoBERTa + LSTM with NYTimes+

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
      \midrule
      GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
      Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
      Transformer (location-aware) & 31.5\% & 36.8\% & 25.3\% & 33.2\% & 23.5\% & 25.3\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      GloVe + LSTM  & 15.3 & 12.3 \\
      Transformer (first 512 tokens)  & 13.1 & 11.7 \\
      Transformer (location-aware) & 13.0 & 11.7  \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
      \midrule
      GloVe + LSTM & 14.0 & 6.09 & 2.98 & 1.67 & 13.0 & 5.15 & 9.96 \\
      RoBERTa + LSTM & 18.6 & 10.1 & 6.03 & 3.88 & 17.1 & 8.00 & 29.2 \\
      Transformer (first 512 tokens) & 17.6 & 10.4 & 6.68 & 4.65 & 19.1 & 8.49 & 41.1 \\
      Transformer (location-aware) & 19.0 & 11.7 & 7.76 & 5.48 & 21.1 & 9.51 & 51.4 \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
      \midrule
      GloVe + LSTM & 10.5\% & 13.1\% & 0\% & 0\% & 0\% & 0\%  \\
      RoBERTa + LSTM & 25.1\% & 26.7\% & 14.8\% & 14.0\% & 12.5\% & 7.98\%  \\
      Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
      Transformer (location-aware) & 31.5\% & 36.8\% & 25.3\% & 33.2\% & 23.5\% & 25.3\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      GloVe + LSTM  & 15.3 & 12.3 \\
      RoBERTa + LSTM  & 15.6 & 13.4 \\
      Transformer (first 512 tokens)  & 13.1 & 11.7 \\
      Transformer (location-aware) & 13.0 & 11.7  \\
		\bottomrule
	\end{tabular}
\end{table*}
